conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-06-20 paper/paper.Rmd
Updated paper introduction

```{r Document Setup}
#| label: setup
#| echo: false
#| message: false
#| warning: false
#| comment: false
knitr::opts_chunk$set(comment = "#>",
                      echo = TRUE,
                      out.width = "95%",
                      retina = 3,
                      fig.height = 4,
                      fig.align = "center",
                      dpi = 300,
                      dev = "png")
options(tinytex.clean = FALSE)
```

@@

Epidemiologists and public policy makers need to understand the dynamics of infectious disease transmission in a population. Identifying vulnerable groups and predicting disease transmission dynamics are essential for informed public health decision-making. Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact". Quantifying social contact and its patterns can provide critical insights into how diseases spread.

We can measure social contact through social contact surveys, where people  describe the number and type of social contact they have. These surveys provide an empirical estimate of the number of social contacts from one age group to another and the setting of contact. For example, we might learn from a contact survey that homes have higher contact between 25-50 year olds and 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.

These surveys exist for a variety of countries, for example, @mossong2008 the "POLYMOD" study, covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands and Poland [@mossong2008]. However, what do we do when we want to look at contact rates in different countries that haven’t been measured? We can use this existing data to help us project to countries or places that do not have empirical survey data. These are called "synthetic contact matrices". A very popular approach by Prem et al projected from the POLYMOD study to 152 countries [@prem2017]. This which was later updated to include contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].

@@

```{r load conmat}
#| label: load-conmat
library(conmat)
perth <- abs_age_lga("Perth (C)")
perth
```

@@

```{r extrapolate polymod}
#| label: extrapolate-polymod
#| echo: true
perth_contact <- extrapolate_polymod(population = perth)
perth_contact
```

@@

```{r autoplot contacts}
#| label: autoplot-contacts
autoplot(perth_contact)
```

@@

>>>>

```{r setup}
#| label: setup
#| echo: false
#| message: false
#| warning: false
#| comment: false
knitr::opts_chunk$set(comment = "#>",
                      echo = TRUE,
                      out.width = "95%",
                      retina = 3,
                      fig.height = 4,
                      fig.align = "center",
                      dpi = 300,
                      dev = "png")
options(tinytex.clean = FALSE)
```

@@

#TODO - A better first sentence that encapsulates conmat use? 
Understanding the dynamics of infectious disease transmission in a population is an important task (?) for epidemiologists and public policy makers.
Identifying vulnerable groups and predicting disease transmission (?)dynamics are essential for informed public health decision-making. Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact". Quantifying social contact and its patterns can provide critical insights into how diseases spread.

We can measure social contact through social contact surveys, where people describe the number and type of social contact they have. These surveys provide (?) a measure of contact rates: an empirical estimate of the number of social contacts from one age group to another and the setting of contact. For example, we might learn from a contact survey that homes have higher contact between 25-50 year olds and 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.

These social contact surveys exist for a few countries. As an example, @mossong2008 the "POLYMOD" study covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008]. However, what do we do when we want to (?)look at/estimate contact rates in different countries that have not been measured? We can use this existing data to help us project to countries or places that do not have empirical survey data. These are called "synthetic contact matrices". A very popular approach by Prem et al projected from the POLYMOD study to 152 countries [@prem2017]. This which was later updated to include contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].

@@

```{r}
#| label: load-conmat
library(conmat)
perth <- abs_age_lga("Perth (C)")
perth
```

@@

```{r}
#| label: extrapolate-polymod
#| echo: true
perth_contact <- extrapolate_polymod(population = perth)
perth_contact
```

@@

```{r}
#| label: autoplot-contacts
autoplot(perth_contact)
```

@@

The results are surveys that can be found in the syncomat package, which can be seen at: https://idem-lab
